### 2015-12-18 outline.tex
add note about uncertainty over retaliation to outline
run example with no retaliation and add notes to outline

\vskip.5in
Median Legislator's Condition
\begin{itemize}
	\item I believe I have to change the legislature's condition to be more like the cheater's payoff for this context
		\[
		  W_{ML}\left( \tau^{AD},\tau^{*a},\ga(e,\ta)\right) > W_{ML}\left( \bta,\ga(e,\ta)\right)
		\]
		\begin{itemize}
			\item Need to make sure this is not always the case.
			\item Median legislator still has to balance (weighted) producers and consumers.
			\item If $\ga = 1$, would pick optimal tariff.
			\item If $\ga$ is so low that $\tau^N < \tau^a$, then agreement will hold. If $\tau^a < \tau^{AD} < \tau^{AD}$, depends on which is closer in welfare terms 
		\end{itemize}
\end{itemize}

>>>>

\vskip.5in
Median Legislator's Condition
\begin{itemize}
	\item I believe I have to change the legislature's condition to be more like the cheater's payoff for this context
		\[
		  W_{ML}\left( \tau^{AD},\tau^{*a},\ga(e,\ta)\right) > W_{ML}\left( \bta,\ga(e,\ta)\right)
		\]
		\begin{itemize}
			\item Need to make sure this is not always the case.
				\begin{itemize}
					\item Median legislator still has to balance (weighted) producers and consumers.
					\item If $\ga = 1$, would pick optimal tariff.
					\item If $\ga$ is so low that $\tau^N < \tau^a$, then agreement will hold. If $\tau^a < \tau^{AD} < \tau^{AD}$, depends on which is closer in welfare terms 
				\end{itemize}
			\item Seems to work okay in Matlab example: just pushes up break probability, trade agreement tariff; reduces gamma and effort (``SOP$\_$example.m'')
			\item Need to check exec's SOC
		\end{itemize}
	\item There could also be uncertainty about the probability that foreign will dispute the AD measure; that could change from the original to the renewal
\end{itemize}
